\color{navyblue} Difference-in-Differences Estimation with Spatial Spillovers

### 2021-05-10 latex/paper/Spillover.tex
Add acknowledgements

\title{\color{navyblue} Difference-in-Differences Estimation with Spatial Spillovers}
\author{\normalsize Kyle Butts\\{\footnotesize Univ. of Colorado, Boulder}}
\date{\footnotesize\today}

>>>>

\title{\color{navyblue} Difference-in-Differences Estimation with Spatial Spillovers\thanks{I am grateful to Taylor Jaworski, Adam McCloskey, Damian Clarke, Daniel Kaffine, Tania Barham, Alexander Bentz, James Flynn, Brach Champion, Hannah Denker, and participants of the CU Boulder Labor Economics Seminar for helpful comments.}}
\author{\normalsize Kyle Butts\\{\footnotesize Univ. of Colorado, Boulder}}
\date{\footnotesize\today}
